High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-11-11 introduction.tex
Fix figure and typo

Face recognition has long been, and continues to be, a highly active area of research \cite{belhumeur2002eigenfaces,yang2002kernel,vasilescu2002multilinear,zhao2003face,he2005face,hua2007face,hua2009robust,guillaumin2009you,hua2009robust,wright2009implicit,zou2007comparative}.
In recent years, interest in the problem of \emph{unconstrained} face
recognition has grown in the community, driven in large part by the creation of
the \emph{Labeled Faces in the Wild (LFW)} \cite{huang:lfw} test set, which has
provided a standardized benchmark against which to measure progress.  While
face recognition research \foreign{per se} has a long and rich history, much
work prior to the last decade was focused on face recognition in relatively
constrained environments (e.g. posed photographs, under controlled  lighting
conditions \cite{orl,yale,cvl,ar,phillips2000feret,gross2009multi}).  More
recently, thanks in large part to the rise of the internet, it has become
possible to assemble large collections of face images ``in the wild'' in the
sense that they come from a wide variety of sources and were not posed for the
purpose of research.  While this set has proven to be quite challenging, large
strides have been in made in recent years towards higher performance
\cite{pinto:eccv08,pinto:cvpr09,taigman:bmvc09,wolf:accv09,kumar:iccv09,cao2010face}.

@@

One potentially promising source for new, more complex visual feature representations is the
class of ``biologically-inspired'' representations.
Biologically-inspired approaches seek to build artificial visual 
systems that capture aspects of the computational architecture of the brain, in the hope of
eventually mimicking its computational abilities. Such efforts to model visual
computations done by the brain have a long history, at least dating back to
Fukushima's Neocognitron (1980; \cite{fukushima1980neocognitron}).  More recent
experiments with biologically-inspired models have shown them to be highly
competitive in a variety of different face and object recognition
contexts \cite{serre2007ror,mutch2008ocr,pinto:plos08,pinto:eccv08,jarrett-iccv-09}.

>>>>

Face recognition has long been, and continues to be, a highly active area of research \cite{belhumeur2002eigenfaces,yang2002kernel,vasilescu2002multilinear,zhao2003face,he2005face,hua2007face,hua2009robust,guillaumin2009you,hua2009robust,wright2009implicit,zou2007comparative}.
In recent years, interest in the problem of \emph{unconstrained} face
recognition has grown in the community, driven in large part by the creation of
the \emph{Labeled Faces in the Wild (LFW)} \cite{huang:lfw} test set, which has
provided a standardized benchmark against which to measure progress.  While
face recognition research \foreign{per se} has a long and rich history, much
work prior to the last decade was focused on face recognition in relatively
constrained environments (e.g. posed photographs, under controlled  lighting
conditions \cite{orl,yale,cvl,ar,phillips2000feret,gross2009multi}).  More
recently, thanks in large part to the rise of the internet, it has become
possible to assemble large collections of face images ``in the wild'' in the
sense that they come from a wide variety of sources and were not posed for the
purpose of research.  While this set has proven to be quite challenging, large
strides have been made in recent years towards higher performance
\cite{pinto:eccv08,pinto:cvpr09,taigman:bmvc09,wolf:accv09,kumar:iccv09,cao2010face}.

@@

One potentially promising source for new, more complex visual feature representations is the
class of ``biologically-inspired'' representations.
These approaches seek to build artificial visual 
systems that capture aspects of the computational architecture of the brain, in the hope of
eventually mimicking its computational abilities. Such efforts to model visual
computations done by the brain have a long history, at least dating back to
Fukushima's Neocognitron (1980; \cite{fukushima1980neocognitron}).  More recent
experiments with biologically-inspired models have shown them to be highly
competitive in a variety of different face and object recognition
contexts \cite{serre2007ror,mutch2008ocr,pinto:plos08,pinto:eccv08,jarrett-iccv-09}.
